%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{xcolor}
\usepackage{hyperref}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Gorusu Yochana Preethi} \\ \vspace{4pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 9347701879 ~ \href{mailto:yochanapreethi2807@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  {yochanapreethi2807@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/yochanapreethi//}{\raisebox{-0.2\height}\faLinkedin\ {\href{}{linkedin/yochanapreethi}}}  ~
    \href{https://github.com/yochanapreethi}{\raisebox{-0.2\height}\faGithub\ {github/yochanapreethi}}
    \vspace{3pt}
    \newline
    \href{https://leetcode.com/u/yochanapreethi/}{\raisebox{-0.2\height}{Leetcode}} ~
    \href{https://www.codechef.com/users/yochanapreethi}{\raisebox{-0.2\height}{Codechef}} ~
    \href{https://www.geeksforgeeks.org/user/yochanapreethi/}{\raisebox{-0.2\height}{GeeksforGeeks}} ~
    \href{https://www.hackerrank.com/yochanapreethi}{\raisebox{-0.2\height}{HackerRank}}
    \vspace{-2pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology, Vellore}{Sep 2022 — May 2026}
      {Bachelor of Technology in Electrical and Electronics Engineering}{Katpadi, Vellore, Tamil Nadu}
      \vspace{-2mm}
      \resumeItemListStart
        \resumeItem{GPA: 8.3/10}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C++, HTML, CSS, JavaScript (beginner)} \\
     \textbf{Data Analytics \& Visualization:} Power BI, Excel, Power Query, Pandas, NumPy, Matplotlib, Seaborn, Jupyter Notebook \\
    \textbf{Tools:} Git, GitHub, VS Code, Figma \\
    \textbf{Database \& Querying:} MySQL}}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeSubheading
    {Zomato Insights Dashboard}{\href{https://github.com/yochanapreethi/zomato_dashboard}{\textcolor{blue}{GitHub}}}
    {Tech stack: Power BI, DAX, Excel, Data Modeling, Power Query}{}
    \resumeItemListStart
      \resumeItem{Built an interactive dashboard to analyze restaurant ratings, delivery trends, and order metrics.}
      \resumeItem{Cleaned and transformed data using Power Query and created calculated measures in DAX.}
    \resumeItemListEnd

    \resumeSubheading
      {Restaurant Ratings and Services Analysis}{\href{https://github.com/yochanapreethi/Restaurant_Ratings_and_Services_Analysis}{\textcolor{blue}{GitHub}}}
      {Tech stack: Python, Pandas, Matplotlib, Seaborn, Jupyter Notebook}{}
      \resumeItemListStart
        \resumeItem{Explored and visualized key restaurant features such as ratings, cuisines, cities, and online delivery impact.}
        \resumeItem{Performed geospatial and categorical analysis to uncover location-based trends and consumer behavior.}
        \resumeItem{Engineered features and analyzed restaurant chains for insights into popularity, rating patterns, and service factors.}
      \resumeItemListEnd

  \resumeSubheading
    {Cisco Sales Performance Analysis}{\href{https://github.com/yochanapreethi/Cisco_Sales_Performance_Analysis}{\textcolor{blue}{GitHub}}}
    {Tech stack: Python, Pandas, Matplotlib, Seaborn, Jupyter Notebook}{}
    \resumeItemListStart
      \resumeItem{Analyzed Cisco stock data to understand trends in opening, closing prices, and volume.}
      \resumeItem{Created visualizations to highlight patterns and fluctuations in stock performance.}
      \resumeItem{Used statistical techniques to explore relationships between price and volume changes.}
    \resumeItemListEnd

  \resumeSubheading
    {Finance Performance Dashboard}{\href{https://github.com/yochanapreethi/finance_dashboard}{\textcolor{blue}{GitHub}}}
    {Tech stack: Power BI, DAX, Excel, Power Query, Data Modeling}{}
    \resumeItemListStart
      \resumeItem{Developed a dashboard to track revenue, expenses, and profit trends.}
      \resumeItem{Implemented drill-throughs and slicers for detailed analysis by time, region, and department.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Zidio}{June 2025 — July 2025}
{Data Analytics Intern}{Remote}
\resumeItemListStart
  \resumeItem{Worked on time series analysis and forecasting for stock market trends.}
  \resumeItem{Leveraged Python and statistical techniques to extract insights from financial datasets.}
\resumeItemListEnd

\resumeSubheading
{CodeAlpha}{June 2025}
{Data Analytics Intern}{Remote}
\resumeItemListStart
  \resumeItem{Performed customer segmentation using exploratory data analysis with Pandas and NumPy.}
  \resumeItem{Analyzed behavioral patterns and churn indicators using frequency and monetary metrics.}
  \resumeItem{Visualized insights using Matplotlib and Seaborn to support business decision-making.}
\resumeItemListEnd

\resumeSubheading
{Visakhapatnam Port Authority}{June 2024 — July 2024}
{Summer Intern}{On-site}
\resumeItemListStart
  \resumeItem{Observed use of RFID, AIS, and radar systems in real-time port logistics and security.}
  \resumeItem{Studied weighbridge operations, dredger and tug systems, and VHF communication tech.}
  \resumeItem{Understood integration of networking technologies including fiber optics for data transmission.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

\end{document}
